\propertitle

### 2020-03-17 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T12:14:41+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

As stated on p.~8, the interpretation is important because it leads to
numerically different results in first- and higher-order approximations.
And such approximations may be necessary in the precise calculation of the
evidence, as explained in the reply to the previous point. Appendix~C
explains where and why the numerical differences appear. Also, it is
important to know whether we are calculating the frequency of past results,
or the probability for a new result, or the most probable frequency of
future results. These three quantities can be numerically very different
when the ratio $\frac{\text{\# samples}}{\text{data-space dimension}}$ is
high, and they are to be used in different ways. Preliminary calculations
from the full Bayesian analysis show that%
\setlength{\intextsep}{-1ex}% with wrapfigure
\setlength{\columnsep}{0ex}% with wrapfigure
\begin{wrapfigure}{r}{0pt} % with wrapfigure
\centering\includegraphics[width=0.5\linewidth]{example_fullbayesian.pdf}
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% exp_family_maxent.nb
the most probable frequency distribution across recorded bins (item i on
p.~8) and the belief distribution over the total activity at any recorded
bin (item ii on p.~8) are visibly different. See figure on the right: item
(i) is the red dashed red curve, item (ii) the solid green line.

These are therefore not philosophical matters. It's a matter of
understanding what we are doing and stating it clearly in our
work. % Unfortunately the
% neuroscience literature is very unclear on such matters.
There's also another important reason. We are generally concerned for
master's and PhD students, who often learn concepts and methods through
actual research, perusing works like the present one. Young researchers too
often end up learning incorrect or confused ideas, gathered from unclear
literature. % They trust it because it's peer-reviewed.
Sometimes the result, quoting Feynman \citey{feynman1985_r1989}, is that
\enquote{they don't learn by understanding; they learn by some other way --
  by rote, or something. Their knowledge is so fragile!}. We owe them
clarity, precision, honesty, and a glimpse of the bigger picture.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-17T16:56:56+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

Perhaps we chose the wrong term, speaking of \enquote{interpretation}. What
we meant is that the formula we find is valid, as a first approximation,
for four different quantities of interest. It is obviously important to
specify for which quantities the formula can be used and, among those, for
which it provides a better or worse approximation.

On p.~8 we also state that first- and higher-order approximations will be
different for each of those four quantities, so their numerical equality is
only valid at zeroth-order. Preliminary calculations from the
full Bayesian%
\setlength{\intextsep}{-1ex}% with wrapfigure
\setlength{\columnsep}{0ex}% with wrapfigure
\begin{wrapfigure}{r}{0pt} % with wrapfigure
\centering\includegraphics[width=0.5\linewidth]{example_fullbayesian.pdf}
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% exp_family_maxent.nb
 analysis show that the most probable frequency distribution across recorded
bins (item i on p.~8) and the belief distribution over the total activity
at any recorded bin (item ii on p.~8) are visibly different. See figure on
the right: item (i) is the red dashed red curve, item (ii) the solid green
line.

Regarding the quantities mentioned on p.~8, it is important to know whether
we are calculating the frequency of past results, or the probability for a
new result, or the most probable frequency of future results. These
quantities can be numerically very different when the ratio
$\frac{\text{\# samples}}{\text{data-space dimension}}$ is high, and they
are to be used in different ways.

These are therefore not philosophical matters. It's a matter of
understanding and clearly stating what we are
calculating. % Unfortunately the
% neuroscience literature is very unclear on such matters.
There's also another important reason. We are generally concerned for
master's and PhD students, who often learn concepts and methods through
actual research, perusing works like the present one. Young researchers too
often end up learning incorrect or confused ideas, gathered from unclear
literature. % They trust it because it's peer-reviewed.
Sometimes the result, quoting Feynman \citey{feynman1985_r1989}, is that
\enquote{they don't learn by understanding; they learn by some other way --
  by rote, or something. Their knowledge is so fragile!}. We owe them
clarity, precision, honesty, and a glimpse of the bigger picture.
